Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-09-14 revision/responseToreviewers.tex

 %, line 539-546) : 'The use of a this metric is justified by the aim of this study that is to find the best association of experimental factors that obtain the lower mean error on all the corpus. The $MAE$ error with logarithmic values allows an equal weight between each difference in sound level and makes it possible to be less sensitive to high energies. It is also a common practice in the environmental acoustics field'.

\item \emph{First, the results obtained when considering fc=20Khz ("fc = 20 kHz is equivalent to consider all the sound mixtures without distinction between traffic and others sound sources") show the lowest MAE for TIR={6,12}, where "the traffic is the main sound source".
--> Have the authors realized the consequences of these results? From these them someone can conclude that it is better to process nothing when interfering sources are 6 and 12 dB lower with respect to the traffic noise level!!}\\
$\rightarrow$ This results suggests that the user does not apply any treatment in cases where road traffic predominates. This is not inconsistent with the purpose of this paper for two reasons: (i) a user would not call for signal processing in situations where road traffic is largely dominating such as in the vicinity of a ring road, (ii) the TIR value is an unknown parameter: the high errors of the filter for negative TIR values discredit its use. We made the precision :
'Even if the performances for the positive $TIR$ values are high, it has to be reminded that in practice, the $TIR$ value is not known. In consequence, without any prior knowledge, this approach cannot be applied.' (please see the beginning of Section 5).

\item \emph{Second, for the remaining studied scenarios, i.e., TIR={-12,-6,0}, the lowest averaged MAE values are obtained by the Sem-NMF, and not by the proposed TI-NMF.
Therefore, from these results, it cannot be concluded that TI-NMF is the best approach in the considered experimental framework. Even more, if you remove from Table 4 the aforementioned values obtained with TIR={-12,-6}, Sem-NMF becomes the best approach with an averaged MAE of 2.12, whereas TI-NMF yield an averaged MAE of 3.14, following the same analysis scheme proposed by the authors.}

$\rightarrow$ We made a precision at the end of section 2 : 'The aim is to find the type of NMF that gives the minimal error on the reconstruction of the traffic noise signal on the whole corpus to be applied to all the different possible urban noise environments.'

@@

$\rightarrow$ The sentence is now rephrased to: 'In this work the non negative matrix factorization framework is used \dots'

\end{enumerate}

\section{Answers to Reviewer 2}

\begin{enumerate}
\item \emph{As the previous work has been already published, the authors should provide references to it and clearly state the new contributions of the presented paper. I believe there may be a substantial overlap with the authors' paper Gloaguena, J. R., Cana, A., Lagrangeb, M., $\&$ Petiotb, J. F. Estimation du niveau sonore du trafic routier au sein de mixtures sonores urbaines par la Factorisation en Matrices Non n\'egatives, 2018.}

$\rightarrow$ The paper 'Gloaguen, J. R., Can, A., Lagrange, M., $\&$ Petiot, J. F. Estimation du niveau sonore du trafic routier au sein de mixtures sonores urbaines par la Factorisation en Matrices Non n\'egatives, 2018' is a congress article without review submitted after the submission of the present paper. It deals with a similar approach but on a different sound corpus.  Furthermore, as it is written in french we chose to alternatively cite 'Gloaguen, J.R., Can, A., Lagrange, M., Petiot, J.F.: Estimating traffic noise levels using acoustic monitoring: A preliminary study' which is written in English and deals with the same corpus.

### 2018-09-14 revision/gloaguenNmfTraffic_v2.tex
fix graphics path

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/bloc_diagram_source_separation.pdf}
\caption{Block diagram of the general source separation model.}
\label{fig:diagram}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/schema_introduction_nmf.pdf}
\caption{NMF decomposition of an urban sound mixture comprising 3 sound events (car passages, car horn and bird's whistles), $\mathbf{W}$ is composed of 3 elements too ($K$ = 3) which correspond to 3 audio spectra (car passages (a), car horn (b) and bird's whistles (c)).}
\label{fig:example_NMF}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{figures/distanceCosLinDisplay.pdf}
\caption{$\mathbf{W}_{traffic}$ extraction from the sorted cosine similarity with a threshold $t = 0.6$. The first $82$ elements are here considered as traffic component.}
\label{fig:W_TI_NMF}
\end{figure}

@@

\begin{figure}[t]
    \centering
       \includegraphics[width=.9\linewidth]{./figures/exampleSimScene}
    \caption{Spectrogram of a sound scene created with \textit{SimScene} software with a sound background (road traffic in green) and 3 sound events (car horn in purple, car passage in red and whistling bird in cyan).}
    \label{fig:example_simScene}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/bloc_diagram_estimator.pdf}
    \caption{Block diagram of the experiment with the urban sound scenes sound mixture step and the estimation step. The estimator may be a frequency low-pass filter or NMF.}
    \label{fig:bloc_experiment}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/bloc_diagram_NMF_EN_2.pdf}
    \caption{Specific block diagram of the NMF estimator with the dictionary design composed from a second sound database.}
    \label{fig:bloc_nmf}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/creation_W_EN.pdf}
\caption{Steps involved in the dictionary learning.}
\label{fig:creation_W}
\end{figure}

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:specW}\includegraphics[width=.45\linewidth]{figures/dictionary3.pdf}}
%  \hspace{5pt}
  \subfloat[]{\label{fig:ElementW}\includegraphics[width=.45\linewidth]{figures/dictionary4.pdf}}
  \caption{Dictionary building on a 3 second extract of a car passage. In dashed lines, a 1 second $w_t$ window  (\ref{fig:specW}). With $w_t$ = 1 second, 3 spectra are then generated and included in $\mathbf{W}$, while for $w_t$ = $all$, the audio file is reduced into 1 spectral vector (\ref{fig:ElementW}).}
  \label{fig:spec_elementW}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{./figures/filter_bar_integrate.pdf}
\caption{Average $MAE$ errors for the LP filter on all the corpus.}
\label{fig:filter_intergate}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \subfloat[$MAE$ error for each $TIR$ and sub-class with the frequency low-pass filter with $f_c$ = 500 Hz.]{\label{fig:TIR_class_filter}\includegraphics[width=0.45\textwidth]{figures/filter_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sup-NMF and $\beta$ = 2.]{\label{fig:TIR_class_sup}\includegraphics[width=0.45\linewidth]{figures/sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sem-NMF and $\beta$ = 1.]{\label{fig:TIR_class_semi}\includegraphics[width=.45\linewidth]{figures/semi-sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with TI-NMF, $\beta$ = 1 and $t$ = 0.41.]{\label{fig:TIR_class_TI}\includegraphics[width=.45\linewidth]{figures/TI_bar}}
  \caption{$MAE$ (dB) error for each sub-class and each $TIR$ according to the best results with the filter (\ref{fig:TIR_class_filter}) and each method (Sup-NMF (\ref{fig:TIR_class_sup}), Sem-NMF (\ref{fig:TIR_class_semi}) and TI-NMF (\ref{fig:TIR_class_TI})).}
	\label{fig:TIR_bar}
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \subfloat[]{\label{fig:specLp}\includegraphics[width=.45\linewidth]{figures/specAlert.pdf}}
%  \hspace{5pt}
  \subfloat[]{\label{fig:lp_alert}\includegraphics[width=.45\linewidth]{figures/NMF_Lp_alert.pdf}}
  \caption{Spectrogram of an \textit{alert} sub-class scene (\ref{fig:specLp}) and evolution of 1 second equivalent sound pressure level (\ref{fig:lp_alert}) for 500 Hz low-pass filter and TI-NMF ($\beta$ = 1, $K$ = 200, $w_t$ = 0.5 s, $t$ = 0.42) at $TIR = -12$ dB (in full line) and $TIR$ = 12 dB (in dashed line).}
  \label{fig:spec_alert}
\end{figure*}

>>>>

\graphicspath{{figures/}{./}}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{bloc_diagram_source_separation.pdf}
\caption{Block diagram of the general source separation model.}
\label{fig:diagram}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{schema_introduction_nmf.pdf}
\caption{NMF decomposition of an urban sound mixture comprising 3 sound events (car passages, car horn and bird's whistles), $\mathbf{W}$ is composed of 3 elements too ($K$ = 3) which correspond to 3 audio spectra (car passages (a), car horn (b) and bird's whistles (c)).}
\label{fig:example_NMF}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{distanceCosLinDisplay.pdf}
\caption{$\mathbf{W}_{traffic}$ extraction from the sorted cosine similarity with a threshold $t = 0.6$. The first $82$ elements are here considered as traffic component.}
\label{fig:W_TI_NMF}
\end{figure}

@@

\begin{figure}[t]
    \centering
       \includegraphics[width=.9\linewidth]{./exampleSimScene}
    \caption{Spectrogram of a sound scene created with \textit{SimScene} software with a sound background (road traffic in green) and 3 sound events (car horn in purple, car passage in red and whistling bird in cyan).}
    \label{fig:example_simScene}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{bloc_diagram_estimator.pdf}
    \caption{Block diagram of the experiment with the urban sound scenes sound mixture step and the estimation step. The estimator may be a frequency low-pass filter or NMF.}
    \label{fig:bloc_experiment}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{bloc_diagram_NMF_EN_2.pdf}
    \caption{Specific block diagram of the NMF estimator with the dictionary design composed from a second sound database.}
    \label{fig:bloc_nmf}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{creation_W_EN.pdf}
\caption{Steps involved in the dictionary learning.}
\label{fig:creation_W}
\end{figure}

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:specW}\includegraphics[width=.45\linewidth]{dictionary3.pdf}}
%  \hspace{5pt}
  \subfloat[]{\label{fig:ElementW}\includegraphics[width=.45\linewidth]{dictionary4.pdf}}
  \caption{Dictionary building on a 3 second extract of a car passage. In dashed lines, a 1 second $w_t$ window  (\ref{fig:specW}). With $w_t$ = 1 second, 3 spectra are then generated and included in $\mathbf{W}$, while for $w_t$ = $all$, the audio file is reduced into 1 spectral vector (\ref{fig:ElementW}).}
  \label{fig:spec_elementW}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{./filter_bar_integrate.pdf}
\caption{Average $MAE$ errors for the LP filter on all the corpus.}
\label{fig:filter_intergate}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \subfloat[$MAE$ error for each $TIR$ and sub-class with the frequency low-pass filter with $f_c$ = 500 Hz.]{\label{fig:TIR_class_filter}\includegraphics[width=0.45\textwidth]{filter_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sup-NMF and $\beta$ = 2.]{\label{fig:TIR_class_sup}\includegraphics[width=0.45\linewidth]{sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sem-NMF and $\beta$ = 1.]{\label{fig:TIR_class_semi}\includegraphics[width=.45\linewidth]{semi-sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with TI-NMF, $\beta$ = 1 and $t$ = 0.41.]{\label{fig:TIR_class_TI}\includegraphics[width=.45\linewidth]{TI_bar}}
  \caption{$MAE$ (dB) error for each sub-class and each $TIR$ according to the best results with the filter (\ref{fig:TIR_class_filter}) and each method (Sup-NMF (\ref{fig:TIR_class_sup}), Sem-NMF (\ref{fig:TIR_class_semi}) and TI-NMF (\ref{fig:TIR_class_TI})).}
	\label{fig:TIR_bar}
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \subfloat[]{\label{fig:specLp}\includegraphics[width=.45\linewidth]{specAlert.pdf}}
%  \hspace{5pt}
  \subfloat[]{\label{fig:lp_alert}\includegraphics[width=.45\linewidth]{NMF_Lp_alert.pdf}}
  \caption{Spectrogram of an \textit{alert} sub-class scene (\ref{fig:specLp}) and evolution of 1 second equivalent sound pressure level (\ref{fig:lp_alert}) for 500 Hz low-pass filter and TI-NMF ($\beta$ = 1, $K$ = 200, $w_t$ = 0.5 s, $t$ = 0.42) at $TIR = -12$ dB (in full line) and $TIR$ = 12 dB (in dashed line).}
  \label{fig:spec_alert}
\end{figure*}
